---
title: "cleaning"
author: "Jacinto"
date: "June 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraryImport, message = FALSE}
library(tidyverse)
library(magrittr)
```



# aisles.csv  
```{r}
aisles <- read_csv("data/aisles.csv")
```
```{r}
aisles
is.na(aisles) %>% sum()
duplicated(aisles) %>% sum()
```

Aisles file is good. Not missing values and no duplicated rows.  


# departments.csv  
```{r}
depart <- read_csv("data/departments.csv")
```
```{r}
depart
```
Looks good. Pretty small so can check by eye.  

# order_products_*.csv 

## prior  
```{r}
orderPrior <- read_csv("data/order_products__prior.csv")
orderPrior %>% dim()
orderPrior %>% head()
```
```{r}
## Find if there are any duplicated rows
duplicated(orderPrior) %>% sum()
## Find if there are any missing values in the set
sapply(orderPrior, FUN = function(x) {sum(is.na(x))})
```

```{r}
orderPrior %>% 
  ggplot(aes(x = add_to_cart_order)) +
  geom_histogram(aes(y = ..density..), binwidth = 2) +
  # geom_freqpoly(aes(y = ..density..)) +
  ## There is no zero value
  xlim(1, NA) + 
  ## very right skewed at the way to 145
  coord_cartesian(xlim = c(1, 30)) +
  labs(title = "Order_products_prior")
```
```{r}
orderPrior %>% 
  ggplot(aes(add_to_cart_order)) +
  geom_density(adjust = 3)  +
  coord_cartesian(xlim = c(1, 30))
```


```{r}
summary(orderPrior$add_to_cart_order)
```

Usually an order that has a large number, the other items are generally large too. Probably not an order for a single person but a group.  

Otherwise order_products__prior.csv looks fine  


## train
```{r}
orderTrain <- read_csv("data/order_products__train.csv")
dim(orderTrain)
orderTrain %>% head()
```
```{r}
summary(orderTrain)
```

```{r}
duplicated(orderTrain) %>% sum()
sapply(orderTrain, FUN = function(x) sum(is.na(x)))
```

```{r}
orderTrain %>% 
  ggplot(aes(x = add_to_cart_order, y = ..density..)) +
  geom_histogram(binwidth = 1) +
  scale_y_continuous(labels = scales::percent_format()) +
  coord_cartesian(xlim = c(1, 30)) +
  labs(title = "Order_Products_Train")
```

prior and train data set looks good.   


# orders.csv  
```{r}
orders <- read_csv("data/orders.csv")
orders %>% dim()
orders %>% head()
```

```{r}
duplicated(orders) %>% sum()
sapply(orders, FUN = function(x) sum(is.na(x)))
```
```{r}
summary(orders)
```

```{r}
## Checking that na for days_since_prior_order just means it is the first order ever  
## Result is number of rows that doesn't have first order as NA
orders %>%
  filter(is.na(days_since_prior_order)) %>% 
  filter(order_number != 1) %>% nrow()
```


```{r}
orders %>% 
  ggplot(aes(days_since_prior_order)) +
  geom_histogram(binwidth = 1) +
  scale_y_continuous(labels = scales::unit_format("k", 1e-3)) +
  labs(title = "Days Since Prior order")
```


orders.csv is good. NA are just the first for all users. And some users have day since prior order is because they ordered again during that day so not a mistake.  



# products  
```{r}
products <- read_csv("data/products.csv")
products %>% dim()
products %>% head()
```

```{r}
duplicated(products) %>% sum()
sapply(products, FUN = function(x) sum(is.na(x)))
```



products.csv is good.  




















































